---
title: "R Notebook Template for Competition"
author: "G2 Group 8"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    number_sections: yes
    theme: readable
    toc: yes
---

```{r global-options, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      fig.height = 6,
                      fig.width = 6,
                      fig.align = "center")
```


# Loading and Exploring the Data Set


Read the data files as usual.
```{r}
train = read.csv("Competition_Train.csv")
test = read.csv("Competition_Test.csv")
```

```{r}
train_before_factor = read.csv("Competition_Train.csv")
test_before_factor = read.csv("Competition_Test.csv")
```

We can convert categorical variables to appropriate types.
```{r}
train$potential_issue = as.factor(train$potential_issue)
train[18:23] = lapply(train[18:23], as.factor)
#str(train)
test$potential_issue = as.factor(test$potential_issue)
test[18:22] = lapply(test[18:22], as.factor)
#str(test)

```


```{r}
library(plyr)
train$potential_issue = revalue(train$potential_issue, c("0"="No", "1"="Yes"))
train[18:23] = lapply(train[18:23], function(x) revalue(x, c("0"="No", "1"="Yes")))
#str(train)
test$potential_issue = revalue(test$potential_issue, c("0"="No", "1"="Yes"))
test[18:22] = lapply(test[18:22], function(x) revalue(x, c("0"="No", "1"="Yes")))
#str(test)
```


```{r echo = TRUE, message = FALSE, warning = FALSE}
library(caret)
library(e1071)
```

Function used to modify the training dataset for logistic regression

```{r}
transform_data = function(data, data_before) {
  #risk_flag_sum = rowSums(data_before[, c("deck_risk", "oe_constraint", "ppap_risk", "stop_auto_buy","rev_stop")])
  #data$risk_flag = risk_flag_sum
  #data = subset(data, select = -c(deck_risk,oe_constraint,ppap_risk,stop_auto_buy,rev_stop))
  data$inventory_turnover_ratio1 <- ifelse((data$national_inv + data$in_transit_qty) == 0, 0, data$sales_1_month / ((data$national_inv + data$in_transit_qty) / 2))
  #data$risk_flag = data$risk_flag - data_before$deck_risk
  data$inventory_compliance <- ifelse(data$national_inv >= data$min_bank, 1, 0)  
  data$inventory_enough <- ifelse(data$national_inv >= data$lead_time*(data$forecast_3_month/90), 1, 0)
  data$neg_inv<-ifelse(data$national_inv <0, 0, 1)
  data$ever_backordered <- ifelse(data$sales_1_month == 0 & data$sales_3_month == 0 & data$sales_6_month == 0 & data$sales_9_month == 0, 1, 0)
  return(data)
}
```

Function used to modify training dataset for linear regression

```{r}
get_linear_data = function(data_before){
  lm_data = data_before
  lm_data = transform_data(lm_data, data_before)
  return(lm_data)
}
```

set training data 
```{r}
train = transform_data(train, train_before_factor)
colnames(train)
```
set linear data
```{r}
lm_data = get_linear_data(train_before_factor)
colnames(lm_data)
```
fit linear model
```{r}
for_3_formula = as.formula(
  forecast_3_month ~ . - sku
  -went_on_backorder - inventory_turnover_ratio1 - inventory_compliance
  #- risk_flag 
  - potential_issue - national_inv - neg_inv - ever_backordered   
  )
```


```{r}
lm_model = lm(for_3_formula, lm_data)
train$predict_fore_3 = predict(lm_model, lm_data)
```

Variables used for Logistic Regression

```{r}
formula1 = as.formula(
  went_on_backorder ~ . - sku +lead_time/in_transit_qty 
  #- lead_time
  #- perf_12_month_avg - perf_6_month_avg - sales_1_month - min_bank
  + local_bo_qty*pieces_past_due
  #- forecast_9_month - forecast_3_month
  + sales_6_month / perf_6_month_avg
  #- pieces_past_due
  #- local_bo_qty
  #- potential_issue
  #- risk_flag
  + sales_3_month/forecast_3_month
  + (sales_6_month-sales_3_month-sales_3_month)/sales_3_month
  + (forecast_6_month-forecast_3_month-forecast_3_month)/forecast_3_month
  + pieces_past_due / national_inv
  + sales_3_month/forecast_3_month
  + (perf_12_month_avg - perf_6_month_avg)
  + national_inv/min_bank
)
```


Tools to run random forest in parallel

```{r}
library(foreach)
library(iterators)
library(parallel)
library(doParallel)

```

```{r}
registerDoParallel(cores = 4)
```

cross-validation setting
```{r}
fitControl = trainControl(method = "cv", number = 3, classProbs = TRUE, summaryFunction = twoClassSummary, allowParallel = TRUE, verboseIter = TRUE)
```

mtry = 9 0.9531508
start cross-validation
```{r}
mtryGrid = expand.grid(.mtry = seq(8, 10, by = 1))
set.seed(123)
rfModel = train(formula1, data = train, method = "rf", metric = "ROC", trControl = fitControl, tuneGrid = mtryGrid, ntree = 900, nodesize = 10)
print(rfModel)
bestMtry <- rfModel$bestTune$.mtry
cat("Best mtry:", bestMtry, "\n")
```
without combining risk flag: 0.9537306
```{r}
mtryGrid = expand.grid(.mtry = seq(8, 10, by = 1))
set.seed(123)
rfModel = train(formula1, data = train, method = "rf", metric = "ROC", trControl = fitControl, tuneGrid = mtryGrid, ntree = 900, nodesize = 10)
print(rfModel)
bestMtry <- rfModel$bestTune$.mtry
cat("Best mtry:", bestMtry, "\n")
```



# Preparing the Predictions for Testing

set testing data 
```{r}
test = transform_data(test, test_before_factor)
colnames(test)
```
set linear data
```{r}
lm_data = get_linear_data(test_before_factor)
colnames(lm_data)
```
fit linear model
```{r}
for_formula = as.formula(
  forecast_3_month ~ . - sku  - inventory_turnover_ratio1 - inventory_compliance
  - risk_flag - potential_issue - national_inv
  )
```


```{r}
lm_model = lm(for_formula, lm_data)
#summary(lm_model)
```

```{r}
lm_model = lm(for_formula, lm_data)
test$predict_fore_3 = predict(lm_model, lm_data)
```

```{r}
Pred1 = predict(model1, newdata = test, type = "response")
PredTest1 = data.frame(test$sku, Pred1)
str(PredTest1)
```

```{r}
summary(PredTest1)
```

```{r}
colnames(PredTest1) = c("sku", "went_on_backorder")
str(PredTest1)
write.csv(PredTest1, "Submission.csv", row.names = FALSE)
```