---
title: "R Notebook Template for Competition"
author: "Guo Yufei"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    number_sections: yes
    theme: readable
    toc: yes
---

```{r global-options, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      fig.height = 6,
                      fig.width = 6,
                      fig.align = "center")
```


```{r}
train_before_factor = read.csv("Competition_Train.csv")
missing_values <- any(is.na(train_before_factor))

# Print the result
print(missing_values)
```

```{r}
train = read.csv("Competition_Train.csv")
test = read.csv("Competition_Test.csv")
#str(train)
#str(test)
```


We can convert categorical variables to appropriate types.
```{r}
train$potential_issue = as.factor(train$potential_issue)
train[18:23] = lapply(train[18:23], as.factor)
#str(train)
test$potential_issue = as.factor(test$potential_issue)
test[18:22] = lapply(test[18:22], as.factor)
#str(test)

```


```{r}
library(plyr)
train$potential_issue = revalue(train$potential_issue, c("0"="No", "1"="Yes"))
train[18:23] = lapply(train[18:23], function(x) revalue(x, c("0"="No", "1"="Yes")))
#str(train)
test$potential_issue = revalue(test$potential_issue, c("0"="No", "1"="Yes"))
test[18:22] = lapply(test[18:22], function(x) revalue(x, c("0"="No", "1"="Yes")))
#str(test)
```


```{r echo = TRUE, message = FALSE, warning = FALSE}
library(caret)
library(e1071)
```

- create data

```{r}
risk_flag_sum = rowSums(train_before_factor[, c("deck_risk", "oe_constraint", "ppap_risk", "stop_auto_buy")])
new_feature_data = train
new_feature_data$risk_flag = risk_flag_sum
new_feature_data = subset(new_feature_data, select = -c(deck_risk,oe_constraint,ppap_risk,stop_auto_buy,rev_stop))
new_feature_data$inventory_turnover_ratio1 <- ifelse((train$national_inv + train$in_transit_qty) == 0, 0, train$sales_1_month / ((train$national_inv + train$in_transit_qty) / 2))
diff_forcast = train$forecast_6_month - train$forecast_3_month - train$forecast_3_month
new_feature_data$future_growth = diff_forcast/(train$forecast_3_month+1)
new_feature_data$risk_flag = new_feature_data$risk_flag - train_before_factor$deck_risk
new_feature_data$overdue_factor = new_feature_data$local_bo_qty*new_feature_data$pieces_past_due
new_feature_data = subset(new_feature_data, select = -c(sku,perf_12_month_avg,perf_6_month_avg,lead_time,sales_1_month,min_bank,forecast_6_month,forecast_9_month))
print(colnames(new_feature_data))
```

```{r}
# remove went_on_backorder
predict_col = new_feature_data$went_on_backorder
new_feature_data = subset(new_feature_data, select = -went_on_backorder)
```

- PCA

```{r}
#install.packages("corrr")
#install.packages("FactoMineR")
#install.packages("factoextra")
```


```{r}
library("factoextra")
library('corrr')
library("FactoMineR")
library(corrplot)
feature_temp = new_feature_data
feature_temp$potential_issue = train_before_factor$potential_issue

# data normalize
data_normalized = scale(feature_temp)

# corplot
correlation_matrix = cor(data_normalized)
corrplot(correlation_matrix, method = "circle")

# apply PCA
data.pca <- princomp(correlation_matrix)
summary(data.pca)

data.pca$loadings[, 1:2]

fviz_eig(data.pca, addlabels = TRUE)

# Graph of the variables
fviz_pca_var(data.pca, col.var = "black")

fviz_cos2(data.pca, choice = "var", axes = 1:3)
```
# Perform PCA
pca_result <- prcomp(feature_temp, center = TRUE, scale. = TRUE)

# Access principal components
pcs <- pca_result$x

# Access standard deviations of principal components
sd <- pca_result$sdev

# Access rotation matrix
rotation <- pca_result$rotation



- RFE feature elimination (Too many columns)

- install
install.packages("randomForest")
install.packages("mlbench")

```{r}
# Load required libraries
library("dplyr")
library("faux")
library("DataExplorer")
library("caret")
library("randomForest")
```


```{r}


# Load your dataset
data <- temp_data6

# Create a control function for RFE
control <- rfeControl(functions = rfFuncs, method = "repeatedcv", repeats = 5, number = 10)

x <- data %>% 
  select(-went_on_backorder) %>% 
  as.data.frame()

# Target variable
y <- data$went_on_backorder

# Training: 80%; Test: 20%
set.seed(2021)
inTrain <- createDataPartition(y, p = .80, list = FALSE)[,1]

x_train <- x[ inTrain, ]
x_test  <- x[-inTrain, ]

y_train <- y[ inTrain]
y_test  <- y[-inTrain]

result_rfe1 <- rfe(x = x_train, 
                   y = y_train, 
                   sizes = c(1:20),
                   rfeControl = control)

# Print the results
result_rfe1

# Print the selected features
predictors(result_rfe1)

# Print the results visually
ggplot(data = result_rfe1, metric = "Accuracy") + theme_bw()
ggplot(data = result_rfe1, metric = "Kappa") + theme_bw()

```

```{r}
print(colnames(x_train))
```


