---
title: "R Notebook Template for Competition"
author: "Guo Yufei"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    df_print: paged
    number_sections: yes
    theme: readable
    toc: yes
---

```{r global-options, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      fig.height = 6,
                      fig.width = 6,
                      fig.align = "center")
```


```{r}
train_before_factor = read.csv("Competition_Train.csv")
missing_values <- any(is.na(train_before_factor))

# Print the result
print(missing_values)
```

```{r}
train = read.csv("Competition_Train.csv")
test = read.csv("Competition_Test.csv")
#str(train)
#str(test)
```


We can convert categorical variables to appropriate types.
```{r}
train$potential_issue = as.factor(train$potential_issue)
train[18:23] = lapply(train[18:23], as.factor)
#str(train)
test$potential_issue = as.factor(test$potential_issue)
test[18:22] = lapply(test[18:22], as.factor)
#str(test)

```


```{r}
library(plyr)
train$potential_issue = revalue(train$potential_issue, c("0"="No", "1"="Yes"))
train[18:23] = lapply(train[18:23], function(x) revalue(x, c("0"="No", "1"="Yes")))
#str(train)
test$potential_issue = revalue(test$potential_issue, c("0"="No", "1"="Yes"))
test[18:22] = lapply(test[18:22], function(x) revalue(x, c("0"="No", "1"="Yes")))
#str(test)
```


```{r echo = TRUE, message = FALSE, warning = FALSE}
library(caret)
library(e1071)
```


First, we will define our cross-validation experiment.
```{r}
fitControl = trainControl(method = "cv", number = 10, classProbs = TRUE, summaryFunction = twoClassSummary)
```
The first argument, *method = "cv"*, tells the function to use the cross-validation method. The additional arguments are necessary since we want to use AUC as the performance measure in cross-validation.


```{r}
set.seed(123)
#train(went_on_backorder ~ . - sku, data = train, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```


```{r}
set.seed(123)
#train(went_on_backorder ~ national_inv, data = train, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

- forecast combine

```{r}
temp_data1 = train
temp_data1$forecast_1to3 = train$forecast_3_month
temp_data1$forecast_3to6 = train$forecast_6_month - train$forecast_3_month
temp_data1$forecast_6to9 = train$forecast_9_month - train$forecast_6_month
average_forecast_3 <- mean(temp_data1$forecast_1to3, na.rm = TRUE)
average_forecast_6 <- mean(temp_data1$forecast_3to6, na.rm = TRUE)
average_forecast_9 <- mean(temp_data1$forecast_6to9, na.rm = TRUE)
str(average_forecast_3)
str(average_forecast_6)
str(average_forecast_9)
temp_data1 <- subset(temp_data1, select = -c(forecast_3_month, forecast_6_month, forecast_9_month))
print(names(temp_data1))
```

- sales combine

```{r}
temp_data1$sales_0to1 = train$sales_1_month
temp_data1$sales_1to3 = train$sales_3_month - train$sales_1_month
temp_data1$sales_3to6 = train$sales_6_month - train$sales_3_month
temp_data1$sales_6to9 = train$sales_9_month - train$sales_6_month
average_sale_1 <- mean(temp_data1$sales_0to1, na.rm = TRUE)
average_sale_3 <- mean(temp_data1$sales_1to3, na.rm = TRUE)
average_sale_6 <- mean(temp_data1$sales_3to6, na.rm = TRUE)
average_sale_9 <- mean(temp_data1$sales_6to9, na.rm = TRUE)
str(average_sale_1)
str(average_sale_3)
str(average_sale_6)
str(average_sale_9)
temp_data1 <- subset(temp_data1, select = -c(sales_1_month, sales_3_month, sales_6_month, sales_9_month))
print(names(temp_data1))
```


- rebuild model with new columns
- no sku
```{r}
set.seed(123)
train(went_on_backorder ~ . - sku, data = temp_data1, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```

```{r}
model_tempdata1 = glm(went_on_backorder ~ . - sku, data = temp_data1, family = "binomial")
summary(model_tempdata1)
```

- national_inv

```{r}
set.seed(123)
train(went_on_backorder ~ national_inv, data = train, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")
```


- no sku, rev_stop, stop_auto_buy

```{r}
temp_data2 = temp_data1
temp_data2 = subset(temp_data2, select = -c(rev_stop, stop_auto_buy))
set.seed(123)
model_tempdata1 = glm(went_on_backorder ~ . - sku, data = temp_data2, family = "binomial")
summary(model_tempdata1)
```

```{r}
set.seed(123)
train(went_on_backorder ~ . - sku, data = temp_data2, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")

```

- no sku, perf_12_month

```{r}
temp_data2 = temp_data1
temp_data2 = subset(temp_data2, select = -c(perf_12_month_avg, forecast_6to9,rev_stop))
set.seed(123)
model_tempdata1 = glm(went_on_backorder ~ . - sku, data = temp_data2, family = "binomial")
summary(model_tempdata1)
```

```{r}
set.seed(123)
train(went_on_backorder ~ . - sku, data = temp_data2, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")

```

- no sku, 

```{r}
print(colnames(train))
```



```{r}
temp_data2 = train
temp_data2 = subset(temp_data2, select = -c( sales_9_month , forecast_9_month))
set.seed(123)
model_tempdata1 = glm(went_on_backorder ~ . - sku, data = temp_data2, family = "binomial")
summary(model_tempdata1)
```

```{r}
set.seed(123)
train(went_on_backorder ~ . - sku, data = temp_data2, method = "glm", family = "binomial", trControl = fitControl, metric = "ROC")

```

```{r}
model_tempdata1 = glm(went_on_backorder ~ deck_risk+oe_constraint+ppap_risk+stop_auto_buy+rev_stop, data = temp_data2, family = "binomial")
summary(model_tempdata1)
```


- modify dataset
```{r}
temp_data3 = train
sales_avg = 
temp_data3$transit_rate = train$in_transit_qty / train$lead_time
temp_data3$risk_flag = train$deck_risk+train$oe_constraint+train$ppap_risk+train$stop_auto_buy+train$rev_stop+train$potential_issue

```



Between these two logistic regression models, the first one with all the independent variables performs better in cross-validation. Now, we will retrain the selected model using the whole training set.
```{r}
modelBO = glm(went_on_backorder ~ . - sku, data = train, family = "binomial")
summary(modelBO)
```


# Preparing the Predictions for Testing


Using the selected model, we make the predictions on the test set and save *sku* and the predicted probabilities of backorder in a data frame.
```{r}
PredBO = predict(modelBO, newdata = test, type = "response")
PredTest = data.frame(test$sku, PredBO)
str(PredTest)
```


```{r}
summary(PredTest)
```


Finally, we tally the variable names and save the predictions in a file. The file can be submitted. The argument, *row.names = FALSE*, prevent R from saving additional column with indecies for each row.
```{r}
colnames(PredTest) = c("sku", "went_on_backorder")
str(PredTest)
write.csv(PredTest, "Sample_Submission.csv", row.names = FALSE)
```


